\pdfoutput=1

\documentclass[sigconf,screen=true,anonymous]{acmart} 
% \documentclass[sigconf,screen=true]{acmart} 

%%%%%

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
% \acmDOI{10.475/123_4}
% ISBN
% \acmISBN{123-4567-24-567/08/06}

\acmConference[WWW 2019]{The Web Conference 2019:  The 28th International World Wide Web Conference}{May 13-17, 2019}{San Francisco}
\acmYear{2019}
\copyrightyear{2019}

\settopmatter{printfolios=false,printacmref=true}
\fancyhead{}

% Space hacks
\clubpenalty=10000
\widowpenalty=10000
\usepackage[subtle, wordspacing=normal, tracking=normal, bibnotes, charwidths=normal, leading, indent, lists, paragraphs=normal, mathspacing=normal, bibliography=normal]{savetrees}
\looseness=-1

\usepackage{hyperref}
\usepackage{booktabs} % For formal tables
\usepackage{subfig}
\usepackage[skip=0pt]{caption}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{enumitem}
\usepackage{acronym}
\usepackage{amsmath}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
%\newcommand{\im}[1]{\textcolor{blue}{IM: #1}}
%\newcommand{\mdr}[1]{\textcolor{cyan}{#1}}
\acrodef{LTR}{learning to rank}
\acrodef{ViTOR}{\textit{Visual learning TO Rank}}
\acrodef{SERP}{search engine result page}

\newcommand{\datasetname}{\ac{ViTOR}}
\newcommand{\modelname}{\ac{ViTOR}}
\newcommand{\OK}{@{\mbox{}\hspace*{.25cm}}}

\title{ViTOR: Learning to Rank Web Pages Based on Visual Features}
% \subtitle{An Improved Method and a Dataset}

\author{Bram van den Akker}
\orcid{}
\affiliation{%
  \institution{University of Amsterdam}
  \city{Amsterdam} 
  \country{The Netherlands}
}
\email{bram.vandenakker@student.uva.nl}

\author{Ilya Markov}
\orcid{}
\affiliation{%
  \institution{University of Amsterdam}
  \city{Amsterdam} 
  \country{The Netherlands}  
}
\email{i.markov@uva.nl}

\author{Maarten de Rijke}
\orcid{0000-0002-1086-0202}
\affiliation{%
   \institution{University of Amsterdam}
   \city{Amsterdam} 
   \country{The Netherlands}
}
\email{derijke@uva.nl}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{B. van den Akker et al.}

\begin{document}

%Web page \ac{LTR} based on visual features is a method of ranking (textual) web pages for a query using their visual appearance as (additional) features.  
%
%In this work we improve web page \ac{LTR} based on visual features, a method of ranking web pages for a query using their visual appearance as (additional) features. 
%
%\mdr{In \ac{LTR} web pages using visual features one uses the visual appearance of web pages as (additional) features to rank (textual) web pages in response to a query.}
\begin{abstract}
Features learned from the visual appearance of a web page can help to improve \ac{LTR} performance. 
We introduce the \modelname~model, a multimodal architecture that can be used to combine both visual features and content features in order to create strong \ac{LTR} features. 
We demonstrate the \modelname~model performance by introducing two powerful feature extraction methods that significantly improve the performance of \ac{LTR} with visual features, namely: 
\begin{inparaenum}[(i)]
\item transfer learning from a pre-trained image recognition model, and
\item synthetic generated saliency heatmaps from page snapshots.
\end{inparaenum}\ 
To support our work we also introduce and release the \datasetname~dataset, a rich and diverse dataset for \ac{LTR} with visual features.
\datasetname~consists of visual snapshots, non-visual features and relevance judgments for ClueWeb12 documents and the TREC Web Track.
The visual snapshots are rendered with both styling and images using the Wayback Machine and ClueWeb12 online rendering service.
Using \datasetname, we confirm that visual features can improve \ac{LTR} performance
and show the effectiveness of the newly introduced architecture and visual feature vectors.
% TODO maybe write something about the ability to use visual LTR cheaply.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>  
% \end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}


\keywords{Learning to rank, Visual features}


\maketitle

\input{cikm2018-visual-ltr-01}
\input{cikm2018-visual-ltr-02}
\input{cikm2018-visual-ltr-03}
\input{cikm2018-visual-ltr-04}
\input{cikm2018-visual-ltr-05}
\input{cikm2018-visual-ltr-06}
\input{cikm2018-visual-ltr-07}

\if0
\subsection*{Acknowledgements}
The Spark experiments in this work were carried out on the Dutch national e-infrastructure with the support of SURF Cooperative. Thanks to the Amsterdam Robotics Lab for using their computational resources. Thanks to Jamie Callan and his team for providing access to the online services for ClueWeb12. 

Anonymized.
\fi

\newpage

\bibliographystyle{ACM-Reference-Format}
\bibliography{cikm2018-visual-ltr} 

\end{document}
