\pdfoutput=1

\documentclass[sigconf,screen=true,natbib]{acmart} 
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{iw3c2w3}
\acmConference[WWW '19]{Proceedings of the 2019 World Wide Web Conference}{May 13--17, 2019}{San Francisco, CA, USA}
\acmBooktitle{Proceedings of the 2019 World Wide Web Conference (WWW '19), May 13--17, 2019, San Francisco, CA, USA}
\acmPrice{}
\acmDOI{10.1145/3308558.3313419}
\acmISBN{978-1-4503-6674-8/19/05}

\settopmatter{printfolios=false,printacmref=true}
\fancyhead{}

% Space hacks
%\clubpenalty=10000
%\widowpenalty=10000
%\usepackage[subtle, wordspacing=normal, tracking=normal, bibnotes, charwidths=normal, leading, indent, lists, paragraphs=normal, mathspacing=normal, bibliography=normal]{savetrees}
%\usepackage[subtle]{savetrees}
\looseness=-1

\setlength{\textfloatsep}{6.0pt plus 1.0pt minus 1.0pt}
\setlength{\floatsep}{6.0pt plus 1.0pt minus 1.0pt}
\setlength{\intextsep}{6.0pt plus 1.0pt minus 1.0pt}

\newcommand{\MyParagraph}[1]{\smallskip\indent\emph{#1.} }

\usepackage{hyperref}
\usepackage{booktabs} % For formal tables
\usepackage{subfig}
\usepackage[skip=0pt]{caption}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{acronym}
\usepackage{amsmath}
%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
%\newcommand{\im}[1]{\textcolor{blue}{IM: #1}}
%\newcommand{\mdr}[1]{\textcolor{cyan}{#1}}
\acrodef{LTR}{learning to rank}
\acrodef{ViTOR}{\textit{Visual learning TO Rank}}
\acrodef{SERP}{search engine results page}

\newcommand{\datasetname}{\ac{ViTOR}}
\newcommand{\modelname}{\ac{ViTOR}}
\newcommand{\modelnamef}{\acf{ViTOR}}
\newcommand{\OK}{@{\mbox{}\hspace*{.25cm}}}

\title{ViTOR: Learning to Rank Webpages Based on Visual Features}
% \subtitle{An Improved Method and a Dataset}

\author{Bram van den Akker}
\orcid{}
\affiliation{%
  \institution{University of Amsterdam}
  \city{Amsterdam} 
  \country{The Netherlands}
}
\email{contact@bramvandenakker.nl}

\author{Ilya Markov}
\orcid{}
\affiliation{%
  \institution{University of Amsterdam}
  \city{Amsterdam} 
  \country{The Netherlands}  
}
\email{i.markov@uva.nl}

\author{Maarten de Rijke}
\orcid{0000-0002-1086-0202}
\affiliation{%
   \institution{University of Amsterdam}
   \city{Amsterdam} 
   \country{The Netherlands}
}
\email{derijke@uva.nl}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{B. van den Akker et al.}

\begin{document}

%Webpage \ac{LTR} based on visual features is a method of ranking (textual) webpages for a query using their visual appearance as (additional) features.  
%
%In this work we improve webpage \ac{LTR} based on visual features, a method of ranking webpages for a query using their visual appearance as (additional) features. 
%
%\mdr{In \ac{LTR} webpages using visual features one uses the visual appearance of webpages as (additional) features to rank (textual) webpages in response to a query.}
\begin{abstract}
The visual appearance of a webpage carries valuable information about the page's quality and can be used to improve the performance of \ac{LTR}.
We introduce the \modelname~model that integrates state-of-the-art visual features extraction methods:
(i) transfer learning from a pre-trained image classification model, and
(ii) synthetic saliency heat maps generated from webpage snapshots.
Since there is currently no public dataset for the task of \ac{LTR} with visual features, we also introduce and release the \datasetname~dataset, containing visually rich and diverse webpages.
The \datasetname~dataset consists of visual snapshots, non-visual features and relevance judgments for ClueWeb12 webpages and TREC Web Track queries.
We experiment with the proposed \modelname~model on the \datasetname~dataset
and show that it significantly improves the performance of \ac{LTR} with visual features.
\end{abstract}



\keywords{Learning to rank; Visual features}


\maketitle

\input{www2019-visual-ltr-01}
\input{www2019-visual-ltr-02}
\input{www2019-visual-ltr-03}
\input{www2019-visual-ltr-04}
\input{www2019-visual-ltr-05}
\input{www2019-visual-ltr-06}
\input{www2019-visual-ltr-07}
\input{www2019-visual-ltr-08}

\subsection*{Code and data}

Both the \datasetname~dataset\footnote{\url{https://github.com/Braamling/learning-to-rank-webpages-based-on-visual-features/blob/master/dataset.md}} and the code used to run the experiments in this paper\footnote{\url{https://github.com/Braamling/learning-to-rank-webpages-based-on-visual-features}} are available online.

\subsection*{Acknowledgements}
The Spark experiments in this work were carried out on the Dutch national e-infrastructure with the support of SURF Cooperative. Thanks to the Amsterdam Robotics Lab for using their computational resources. Thanks to Jamie Callan and his team for providing access to the online services for ClueWeb12. 

This research was partially supported by
%
Ahold Delhaize,
%
the Association of Universities in the Netherlands (VSNU),
%
and
%
the Innovation Center for Artificial Intelligence (ICAI).
%
All content represents the opinion of the authors, which is not necessarily shared or endorsed by their respective employers and/or sponsors.


\bibliographystyle{ACM-Reference-Format}
\bibliography{www2019-visual-ltr} 

\end{document}
